---
title: "Corn Simulation Data Analysis"
subtitle: "Exploring yield and water use efficiency across genotypes, planting dates, and water management scenarios"
author: "Lucas Romano"
format: pdf
---

## 1) Data import and setup

Load necessary libraries and import the corn simulation data from the Excel file.
```{r}
library(tidyverse)
library(knitr)
library(stringr)
library(readxl)
# Load the corn simulation data
corn_sim <- read_excel(
  '/Users/lucasromano/Desktop/Crop Modeling/Corn SSM/ssm-model/SSM_iCrop_Maize_realbps.xlsm',
   sheet = "corn_sim")
```

## 2) Data cleaning and feature engineering

Cleaning and preparing the data.
```{r data-cleaning}
corn_sim_clean <- corn_sim %>%
  rename(YEAR = Pyear) %>%
  dplyr::select(-c(R2.BOT, R3.EAR, R4.ANT, R5.BSG, R6.TSG))  %>% 
  dplyr::select(-NLF:-CNDNIT) %>%
  mutate(
    # Categorize water management from Management column
    water_mgmt = case_when(
      str_detect(Manag, "RFD") ~ "Rainfed",
      str_detect(Manag, "IRRI") ~ "Irrigated",
      TRUE ~ "Unknown"
    ),
    # Extract VPD response: Check vs LT (Limited Transpiration) genotypes
    vpd_response = case_when(
      str_detect(Crop, regex("check", ignore_case = TRUE)) ~ "Check",
      str_detect(Crop, regex("LT", ignore_case = TRUE)) ~ "LT"
    ),
    # Categorize planting date from scenario name
    Planting_date = case_when(
      str_detect(sName, "ELY") ~ "Early",
      str_detect(sName, "MID") ~ "Medium",
      str_detect(sName, "LTE") ~ "Late",
      TRUE ~ "Unknown"
    ),
    # Calculate water loss (runoff + evaporation + transpiration + drainage)
    WLOSS = CRUNOF + CE + CTR + CDRAIN,
    # Convert grain yield to kg/ha (WGRN is in smaller units)
    Yield_kgha = WGRN * 10,
    # Calculate Water Use Efficiency (yield per unit transpiration)
    WUE = Yield_kgha / ET,
    # Assign state based on location
    State = case_when(
      Location %in% c("Marianna", "Jonesboro", "Stuttgart") ~ "Arkansas",
      Location %in% c("Norfolk", "Lincoln", "North Platte") ~ "Nebraska",
      TRUE ~ "Other"
    )
  ) 
```

## 3) Data subsets

Data subsets for rainfed and irrigated scenarios.
```{r}
rainfed_data <- corn_sim_clean %>%
  filter(water_mgmt == "Rainfed")

irrigated_data <- corn_sim_clean %>%
  filter(water_mgmt == "Irrigated")
```

Data subsets for early, medium, and late planting dates.
```{r}
early_planting <- corn_sim_clean %>%
  filter(Planting_date == "Early")
medium_planting <- corn_sim_clean %>%
  filter(Planting_date == "Medium")
late_planting <- corn_sim_clean %>%
  filter(Planting_date == "Late")
```

Data subsets for Check and LT genotypes.
```{r}
check_genotypes <- corn_sim_clean %>%
  filter(vpd_response == "Check")
lt_genotypes <- corn_sim_clean %>%
  filter(vpd_response == "LT")
```

Data subsets for locations in Arkansas and Nebraska.
```{r}
marianna_data <- corn_sim_clean %>%
  filter(Location == "Marianna")

jonesboro_data <- corn_sim_clean %>%
  filter(Location == "Jonesboro")

stuttgart_data <- corn_sim_clean %>%
  filter(Location == "Stuttgart")

norfolk_data <- corn_sim_clean %>%
  filter(Location == "Norfolk")

lincoln_data <- corn_sim_clean %>%
  filter(Location == "Lincoln")

north_platte_data <- corn_sim_clean %>%
  filter(Location == "North Platte")
```

## 4) Exploratory summaries and baseline comparisons

Rainfed scenarios. 
```{r}
# Summary statistics for yield and water use efficiency by water
# management and planting date
summary_stats <- corn_sim_clean %>%
  group_by(water_mgmt, Planting_date) %>%
  summarise(
    mean_yield = mean(Yield_kgha, na.rm = TRUE),
    sd_yield = sd(Yield_kgha, na.rm = TRUE),
    mean_wue = mean(WUE, na.rm = TRUE),
    sd_wue = sd(WUE, na.rm = TRUE)
  )
kable(
  summary_stats, 
  caption = "Summary Statistics for Yield and Water Use Efficiency
  by Water Management and Planting Date")

# Boxplot of yield by water management and planting date
ggplot(corn_sim_clean,
 aes(
  x = factor(
    Planting_date, levels = c("Early", "Medium", "Late")),
     y = Yield_kgha, fill = water_mgmt)) +
  geom_boxplot() +
  labs(title = "Grain Yield by Planting Date and Water Management",
       x = "Planting Date",
       y = "Grain Yield (kg/ha)",
       fill = "Water Management") +
  theme_minimal()


# Boxplot of water use efficiency by water management and planting date
ggplot(
  corn_sim_clean, aes(
    x = factor(Planting_date, levels = c("Early", "Medium", "Late")),
    y = WUE, fill = water_mgmt)) +
  geom_boxplot() +
  labs(title = "Water Use Efficiency by Planting Date and Water Management",
       x = "Planting Date",
       y = "Water Use Efficiency (kg/ha per mm ET)",
       fill = "Water Management") +
  theme_minimal()

# Compare WUE between Check and LT genotypes at Late planting date
corn_sim_clean %>%
  filter(Planting_date == "Late" & 
  Crop %in% c("Maize-AR-check","Maize-AR-LT-1.2")) %>%
  ggplot(aes(x = Crop, y = WUE, fill = Crop)) +
  geom_boxplot() +
  facet_wrap(~ water_mgmt) +
  scale_x_discrete(
    labels = c("Maize-AR-check" = "Check", "Maize-AR-LT-1.2" = "LT 1.2")) +
  labs(title = "WUE: Check vs LT Genotypes at Late Planting Date",
       x = "Genotype",
       y = "Water Use Efficiency (kg/ha per mm ET)",
       fill = "Genotype") +
  theme_minimal()

# Analyze yield differences between Check and LT genotypes in North Platte
corn_sim_clean %>%
  filter(
    Crop %in% c("Maize-NE-check","Maize-NE-LT-1.8") &
    Location %in% c("North Platte")) %>%
  ggplot(aes(x = Crop, y = Yield_kgha, fill = Crop)) +
  geom_boxplot() +
  facet_wrap(~ water_mgmt) +
  scale_x_discrete(
    labels = c("Maize-NE-check" = "Check", "Maize-NE-LT-1.8" = "LT 1.8")) +
  labs(title = "Yield: Check vs LT Genotypes in North Platte",
       x = "Genotype",
       y = "Grain Yield (kg/ha)",
       fill = "Genotype") +
  theme_minimal()

```

### 4.1) Rainfed scenarios

Average yields by location.
```{r}
avg_yields_location <- rainfed_data %>%
  group_by(Location) %>%
  summarise(
    mean_yield = mean(Yield_kgha, na.rm = TRUE),
    sd_yield = sd(Yield_kgha, na.rm = TRUE),
    n = dplyr::n(),
    .groups = "drop"
  )
knitr::kable(avg_yields_location, caption = "Average Yields by Location (kg/ha)")  
```

Average yields by planting date.
```{r}
avg_yields_planting <- rainfed_data %>%
mutate(Planting_date = factor(
  Planting_date, levels = c("Early", "Medium", "Late"))) %>%
  group_by(Planting_date) %>%
  summarise(
    mean_yield = mean(Yield_kgha, na.rm = TRUE),
    sd_yield = sd(Yield_kgha, na.rm = TRUE),
    n = dplyr::n(),
    .groups = "drop"
  )
knitr::kable(avg_yields_planting, caption = "Average Yields by Planting Date (kg/ha)")  
```

Average yields by genotypes.
```{r}
avg_yields_genotypes_AR <- rainfed_data %>%
  filter(Location %in% c("Marianna", "Jonesboro", "Stuttgart")) %>%
  group_by(Crop) %>%
  summarise(
    mean_yield = mean(Yield_kgha, na.rm = TRUE),
    sd_yield = sd(Yield_kgha, na.rm = TRUE),
    n = dplyr::n(),
    .groups = "drop"
  )
knitr::kable(avg_yields_genotypes_AR, caption = "Average Yields by Genotypes
in Arkansas (Check vs LT) (kg/ha)") 

avg_yields_genotypes_NE <- rainfed_data %>%
  filter(Location %in% c("North Platte","Lincoln","Norfolk")) %>%
  group_by(Crop) %>%
  summarise(
    mean_yield = mean(Yield_kgha, na.rm = TRUE),
    sd_yield = sd(Yield_kgha, na.rm = TRUE),
    n = dplyr::n(),
    .groups = "drop"
  )
knitr::kable(avg_yields_genotypes_NE, caption = "Average Yields by Genotypes
in Nebraska (Check vs LT) (kg/ha)")  
``` 

## 5) Weather data processing

Process historical weather data (1990-2019) for growing season (DOY 115-250).
Classify weather years as: Cool/Wet, Warm/Wet, Normal, Cool/Dry, Warm/Dry.
```{r weather-data-processing}
  # Function to process weather data for a location
  process_weather_data <- function(file_path, location_name) {
    read_excel(file_path, sheet = "Sheet2") %>% 
      filter(between(DOY, 115, 250), between(YEAR, 1990, 2019)) %>%
      mutate(MeanT = (TMAX + TMIN) / 2) %>% 
      group_by(YEAR) %>% 
      summarise(Rain = sum(RAIN, na.rm = TRUE),
                Meat = mean(MeanT, na.rm = TRUE),
                .groups = "drop") %>% 
      mutate(
        Rain.avg = mean(Rain),
        Meat.avg = mean(Meat),
        Rain.sd = sd(Rain),
        Meat.sd = sd(Meat),
        Normal = ifelse(Rain < Rain.avg + Rain.sd * 0.5 & Rain > Rain.avg - Rain.sd * 0.5 &
                        Meat < Meat.avg + Meat.sd * 0.5 & Meat > Meat.avg - Meat.sd * 0.5,
                        "Yes", "No"),
        Rain.class = ifelse(Rain > Rain.avg, "Wet", "Dry"),
        Meat_class = ifelse(Meat > Meat.avg, "Warm", "Cool"),
        weather.class = factor(
          ifelse(Normal == "Yes", "Normal", paste0(Meat_class, "/", Rain.class)),
          levels = c("Cool/Wet", "Warm/Wet", "Normal", "Cool/Dry", "Warm/Dry")
        ),
        Location = location_name
      )
  }

  # Define file paths and locations
  weather_files <- list(
    Jonesboro = '/Users/lucasromano/Desktop/Crop Modeling/Weather/AR-ARTJBR_Jonesboro.xlsx',
    Stuttgart = '/Users/lucasromano/Desktop/Crop Modeling/Weather/AR-AR6920_Stuttgart.xlsx',
    Marianna = '/Users/lucasromano/Desktop/Crop Modeling/Weather/AR-AR4638_Marianna.xlsx',
    Lincoln = '/Users/lucasromano/Desktop/Crop Modeling/Weather/NE_Lincoln.xlsx',
    `North Platte` = '/Users/lucasromano/Desktop/Crop Modeling/Weather/NE-NE6075_NorthPlate_Nebraska.xlsx',
    Norfolk = '/Users/lucasromano/Desktop/Crop Modeling/Weather/NE_Norfolk.xlsx'
  )

  # Process all locations and bind together
  RAIN_ALL <- map_df(names(weather_files), ~process_weather_data(weather_files[[.x]], .x)) 
```

## 6) Merge simulation and weather classes

Join weather classification (Cool/Wet, Warm/Dry, etc.) to each year's yield data.
```{r data-merge}
corn_sim_classes <- left_join(x = corn_sim_clean,y = RAIN_ALL, by = c("YEAR","Location"))
```


## 7) Year-by-year yield advantage (LT-1.8 vs Check)

```{r}
analyze_site_lt18 <- function(site_name) {
  site_dat <- rainfed_data %>% 
    filter(Location == site_name)
  
  by_year <- site_dat %>% 
    mutate(geno = case_when(
      str_detect(Crop, regex("check", ignore_case = TRUE)) ~ "Check",
      str_detect(Crop, regex("LT[-_\\.]?1\\.8|\\b1\\.8\\b", ignore_case = TRUE)) ~ "LT1.8",
      TRUE ~ NA_character_
    )) %>% 
    filter(!is.na(geno), !is.na(Yield_kgha)) %>%
    group_by(YEAR, geno) %>% 
    summarise(yld = mean(Yield_kgha, na.rm = TRUE), .groups = "drop") %>%
    pivot_wider(
      names_from = geno,
      values_from = yld,
      values_fill = list(yld = NA_real_)
    ) %>% 
    mutate(pct_increase = (`LT1.8` - Check) / Check * 100)
  
  by_year_joined <- left_join(
    by_year,
    RAIN_ALL %>% dplyr::select(YEAR, Location, Rain.class) %>% filter(Location == site_name),
    by = "YEAR"
  )
  
  avg_check <- mean(by_year_joined$Check, na.rm = TRUE)
  avg_lt18  <- mean(by_year_joined$`LT1.8`, na.rm = TRUE)
  print(paste(site_name, "mean Check yield:", round(avg_check, 2)))
  print(paste(site_name, "mean LT1.8 yield:", round(avg_lt18, 2)))
  
  p <- ggplot(by_year_joined, aes(x = YEAR, y = pct_increase, colour = Rain.class)) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_linerange(aes(ymin = 0, ymax = pct_increase)) +
    geom_point(size = 2) +
    labs(
      title = paste0("Percentage Yield Increase of LT1.8 vs Check in ", site_name, " (Rainfed)"),
      x = "Year",
      y = "Yield increase (%)",
      colour = "Rain Class"
    ) +
    theme_minimal(base_size = 12)
  
  print(p)
  
  output_dir <- "/Users/lucasromano/Desktop/Crop Modeling/Corn SSM/graphs, tables and diagrams"
  file_stub <- gsub(" ", "", site_name)
  ggsave(
    filename = file.path(output_dir, paste0(file_stub, "_RFD_LT18_vs_Check.tiff")),
    p,
    width = 7,
    height = 4,
    dpi = 300,
    device = "tiff"
  )
  
  invisible(by_year_joined)
}

site_results <- list(
  Norfolk = analyze_site_lt18("Norfolk"),
  Jonesboro = analyze_site_lt18("Jonesboro"),
  Marianna = analyze_site_lt18("Marianna"),
  Stuttgart = analyze_site_lt18("Stuttgart"),
  `North Platte` = analyze_site_lt18("North Platte"),
  Lincoln = analyze_site_lt18("Lincoln")
)
```


## 8) Plotting functions and utilities
```{r plot-utilities}
# ---- CROP LABEL MAPPING ----
# Simplify crop names in plot labels (e.g., "Maize-AR-check" → "Check")
crop_labels <- c(
  "Maize-AR-check" = "Check",
  "Maize-AR-LT-1.2" = "1.2",
  "Maize-AR-LT-1.8" = "1.8",
  "Maize-AR-LT-2.1" = "2.1",
  "Maize-AR-LT-2.3" = "2.3",
  "Maize-AR-LT-3.7" = "3.7",
  "Maize-NE-check" = "Check",
  "Maize-NE-LT-1.2" = "1.2",
  "Maize-NE-LT-1.8" = "1.8",
  "Maize-NE-LT-2.1" = "2.1",
  "Maize-NE-LT-2.3" = "2.3",
  "Maize-NE-LT-3.7" = "3.7"
)
# ---- FUNCTION: Plot yield by crop × water management ----
# Generates bar chart with error bars (Standard Error) for a given location
output_dir <- "/Users/lucasromano/Desktop/Crop Modeling/Corn SSM/graphs, tables and diagrams"

plot_yield_summary <- function(location_data, location_name, filename) {
  # Calculate summary statistics (mean ± SE) by crop and water management
  summary_data <- location_data %>%
    group_by(Crop, water_mgmt) %>%
    summarise(
      mean_yield = mean(Yield_kgha, na.rm = TRUE),
      sd_yield = sd(Yield_kgha, na.rm = TRUE),
      n = n(),
      se_yield = sd_yield / sqrt(n),
      .groups = "drop"
    )

  # Create visualization with grouped bars and error bars
  p <- ggplot(summary_data, aes(x = Crop, y = mean_yield, fill = water_mgmt)) +
    geom_col(position = position_dodge(width = 0.9)) +             # Grouped columns
    geom_errorbar(                                                 # Standard error bars
      aes(ymin = mean_yield - se_yield, ymax = mean_yield + se_yield),
      position = position_dodge(width = 0.9),
      width = 0.3
    ) +
    scale_x_discrete(labels = crop_labels) +                      # Use short labels
    scale_y_continuous(limits = c(0, 15000)) +                 # Fixed y-axis range
    labs(
      title = paste("Yield across BP and Water Management in", location_name),
      x = "TR Breakpoint (kPa)",
      y = "Yield (kg/ha)"
    ) +
    theme_bw()

  # Save and display
  ggsave(file.path(output_dir, filename), p, width = 9, height = 6, dpi = 300, device = "tiff")
  print(p)
}

# ---- EXAMPLE: Norfolk Yield Plot ----
plot_yield_summary(norfolk_data, "Norfolk", "YxBPxWM_Norfolk.tiff")
plot_yield_summary(jonesboro_data, "Jonesboro", "YxBPxWM_Jonesboro.tiff")
plot_yield_summary(marianna_data, "Marianna", "YxBPxWM_Marianna.tiff")
plot_yield_summary(stuttgart_data, "Stuttgart", "YxBPxWM_Stuttgart.tiff")
plot_yield_summary(north_platte_data, "North Platte", "YxBPxWM_NorthPlatte.tiff")
plot_yield_summary(lincoln_data, "Lincoln", "YxBPxWM_Lincoln.tiff")
```


## 9) Water use efficiency (WUE) analysis

Analyze yield response to cumulative transpiration (CTR) for different regions.

# ---- WUE: shared utilities ----
```{r wue-setup}
library(ggplot2)
library(ggpmisc)

build_wue_plot <- function(data, water_mode, crop_ids, plot_title, color_var = NULL) {
  plot_data <- data %>%
    filter(
      water_mgmt == water_mode,
      Crop %in% crop_ids
    )

  if (is.null(color_var)) {
    p <- ggplot(plot_data, aes(x = CTR, y = Yield_kgha))
  } else {
    p <- ggplot(plot_data, aes(x = CTR, y = Yield_kgha, color = .data[[color_var]]))
  }

  p +
    geom_point(alpha = 0.7, size = 2) +
    geom_smooth(method = "lm", se = FALSE, linetype = "solid", linewidth = 1.1) +
    stat_poly_eq(
      aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
      formula = y ~ x,
      parse = TRUE,
      label.x.npc = "left",
      label.y.npc = 0.95,
      size = 3
    ) +
    facet_wrap(~Crop, scales = "fixed") +
    labs(
      title = plot_title,
      x = "Cumulative Transpiration (mm)",
      y = "Grain Yield (kg ha⁻¹)"
    ) +
    theme_bw(base_size = 13) +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      legend.position = "top",
      strip.background = element_rect(fill = "grey90"),
      strip.text = element_text(face = "bold")
    )
}

save_wue_plot <- function(plot_obj, filename) {
  ggsave(
    filename = filename,
    plot = plot_obj,
    width = 9,
    height = 4,
    dpi = 300,
    device = "tiff"
  )
}
```

# ---- WUE: all scenarios using one loop ----
```{r wue-scenarios}
wue_scenarios <- list(
  list(
    obj_name = "WUE_AR_Irrigated",
    data_obj = corn_sim_clean,
    water_mode = "Irrigated",
    crop_ids = c("Maize-AR-check", "Maize-AR-LT-1.8"),
    title = "Yield Response to Cumulative Transpiration in Arkansas (Irrigated)",
    color_var = "Crop",
    file_name = "WUE_AR_Irrigated.tiff"
  ),
  list(
    obj_name = "WUE_AR_Rainfed",
    data_obj = corn_sim_clean,
    water_mode = "Rainfed",
    crop_ids = c("Maize-AR-check", "Maize-AR-LT-1.8"),
    title = "Yield Response to Cumulative Transpiration in Arkansas (Rainfed)",
    color_var = NULL,
    file_name = "WUE_AR_Rainfed.tiff"
  ),
  list(
    obj_name = "WUE_NE_Rainfed",
    data_obj = corn_sim_clean,
    water_mode = "Rainfed",
    crop_ids = c("Maize-NE-check", "Maize-NE-LT-1.8"),
    title = "Yield Response to Cumulative Transpiration in Nebraska (Rainfed)",
    color_var = NULL,
    file_name = "WUE_NE_Rainfed.tiff"
  ),
  list(
    obj_name = "WUE_NE_Irrigated",
    data_obj = corn_sim_clean,
    water_mode = "Irrigated",
    crop_ids = c("Maize-NE-check", "Maize-NE-LT-1.8"),
    title = "Yield Response to Cumulative Transpiration in Nebraska (Irrigated)",
    color_var = NULL,
    file_name = "WUE_NE_Irrigated.tiff"
  )
)

output_dir <- "/Users/lucasromano/Desktop/Crop Modeling/Corn SSM/graphs, tables and diagrams"

for (scenario in wue_scenarios) {
  wue_plot <- build_wue_plot(
    data = scenario$data_obj,
    water_mode = scenario$water_mode,
    crop_ids = scenario$crop_ids,
    plot_title = scenario$title,
    color_var = scenario$color_var
  )

  assign(scenario$obj_name, wue_plot)
  save_wue_plot(wue_plot, file.path(output_dir, scenario$file_name))
}
```


## 10) Yield stability analysis

Compare year-to-year variability (CV) in yields for Check vs LT genotypes.

```{r yield-stab-setup}
library(dplyr)
library(ggplot2)

build_stability_data <- function(data, water_mode, g1, g2, label_map = NULL) {
  df_year <- data %>%
    filter(water_mgmt == water_mode, Crop %in% c(g1, g2)) %>%
    group_by(Crop, YEAR) %>%
    summarise(y = mean(Yield_kgha, na.rm = TRUE), .groups = "drop")

  if (is.null(label_map)) {
    df_year <- df_year %>% mutate(Crop_pretty = Crop)
  } else {
    df_year <- df_year %>% mutate(Crop_pretty = as.character(label_map[Crop]))
  }

  stab <- df_year %>%
    group_by(Crop, Crop_pretty) %>%
    summarise(
      mean_y = mean(y),
      sd_y = sd(y),
      cv = 100 * sd_y / mean_y,
      .groups = "drop"
    )

  subtxt <- stab %>%
    mutate(lbl = sprintf("%s: mean = %.0f kg/ha, CV = %.1f%%", Crop_pretty, mean_y, cv)) %>%
    pull(lbl) %>%
    paste(collapse = "   |   ")

  list(df_year = df_year, stab = stab, subtxt = subtxt)
}

plot_stability_basic <- function(stab_obj, title_text) {
  ggplot(stab_obj$df_year, aes(x = YEAR, y = y, color = Crop_pretty, group = Crop_pretty)) +
    geom_line(linewidth = 1) +
    geom_point() +
    geom_hline(
      data = stab_obj$stab,
      aes(yintercept = mean_y, color = Crop_pretty),
      linetype = "dashed",
      linewidth = 0.8,
      show.legend = FALSE
    ) +
    labs(
      title = title_text,
      subtitle = stab_obj$subtxt,
      x = "Year",
      y = "Yield (kg/ha)",
      color = "Genotype"
    ) +
    theme_bw()
}

plot_stability_poster <- function(stab_obj, title_text, palette) {
  ggplot(
    stab_obj$df_year,
    aes(x = YEAR, y = y, color = Crop_pretty, group = Crop_pretty)
  ) +
    geom_line(linewidth = 1.4) +
    geom_point(size = 3, stroke = 1, fill = "white", shape = 21, show.legend = FALSE) +
    geom_hline(
      data = stab_obj$stab,
      aes(yintercept = mean_y, color = Crop_pretty),
      linetype = "dashed",
      linewidth = 1,
      show.legend = FALSE
    ) +
    scale_color_manual(values = palette, name = "Genotype") +
    scale_y_continuous(labels = function(x) format(x, big.mark = ",", scientific = FALSE)) +
    labs(
      title = title_text,
      subtitle = stab_obj$subtxt,
      x = "Year",
      y = "Yield (kg ha⁻¹)",
      color = "Genotype"
    ) +
    theme_minimal(base_size = 15, base_family = "Helvetica") +
    theme(
      plot.title = element_text(size = 20, face = "bold", hjust = 0.5, lineheight = 1.1,
      margin = margin(b = 6)),
      plot.subtitle = element_text(size = 14, hjust = 0.5, margin = margin(b = 12)),
      axis.title = element_text(size = 16, face = "bold"),
      axis.text = element_text(size = 14),
      axis.line.x = element_line(linewidth = 0.8, color = "black"),
      axis.line.y = element_line(linewidth = 0.8, color = "black"),
      panel.grid.major.y = element_line(color = "gray85", linewidth = 0.6),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      legend.position = "top",
      legend.title = element_text(size = 14, face = "bold"),
      legend.text = element_text(size = 13),
      plot.margin = margin(15, 20, 15, 20)
    )
}

save_stability_plot <- function(plot_obj, file_name, width, height, dpi) {
  ggsave(
    filename = file.path(output_dir, file_name),
    plot = plot_obj,
    width = width,
    height = height,
    dpi = dpi,
    compression = "lzw",
    device = "tiff"
  )
}
```

```{r yield-stab-scenarios}
stability_scenarios <- list(
  list(
    obj_name = "Ystab_AR_rfd",
    water_mode = "Rainfed",
    g1 = "Maize-AR-check",
    g2 = "Maize-AR-LT-1.8",
    label_map = c("Maize-AR-check" = "Check", "Maize-AR-LT-1.8" = "LT 1.8"),
    style = "poster",
    palette = c("Check" = "#7570b3", "LT 1.8" = "#d95f02"),
    title = "Yield stability across 30 years\nArkansas · Rainfed management",
    file_name = "Ystab_AR_rfd_poster.tiff",
    width = 10,
    height = 6,
    dpi = 600
  ),
  list(
    obj_name = "Ystab_AR_irri",
    water_mode = "Irrigated",
    g1 = "Maize-AR-check",
    g2 = "Maize-AR-LT-1.8",
    label_map = NULL,
    style = "basic",
    palette = NULL,
    title = "Yield stability across 30 years, in Arkansas, Irrigated",
    file_name = "Ystab_AR_irri.tiff",
    width = 9,
    height = 4,
    dpi = 300
  ),
  list(
    obj_name = "Ystab_NE_rfd",
    water_mode = "Rainfed",
    g1 = "Maize-NE-check",
    g2 = "Maize-NE-LT-1.8",
    label_map = NULL,
    style = "basic",
    palette = NULL,
    title = "Yield stability across 30 years, in Nebraska, Rainfed",
    file_name = "Ystab_NE_rfd.tiff",
    width = 9,
    height = 4,
    dpi = 300
  ),
  list(
    obj_name = "Ystab_NE_irri",
    water_mode = "Irrigated",
    g1 = "Maize-NE-check",
    g2 = "Maize-NE-LT-1.8",
    label_map = c("Maize-NE-check" = "Check", "Maize-NE-LT-1.8" = "LT 1.8"),
    style = "poster",
    palette = c("Check" = "#0072B2", "LT 1.8" = "#E69F00"),
    title = "Yield stability across 30 years\nNebraska · Irrigated management",
    file_name = "Ystab_NE_irri_poster.tiff",
    width = 10,
    height = 5,
    dpi = 600
  )
)

for (scenario in stability_scenarios) {
  stab_obj <- build_stability_data(
    data = corn_sim_clean,
    water_mode = scenario$water_mode,
    g1 = scenario$g1,
    g2 = scenario$g2,
    label_map = scenario$label_map
  )

  stab_plot <- if (scenario$style == "poster") {
    plot_stability_poster(stab_obj, scenario$title, scenario$palette)
  } else {
    plot_stability_basic(stab_obj, scenario$title)
  }

  assign(scenario$obj_name, stab_plot)
  save_stability_plot(
    plot_obj = stab_plot,
    file_name = scenario$file_name,
    width = scenario$width,
    height = scenario$height,
    dpi = scenario$dpi
  )

  print(stab_plot)
}
```

